Packet-by-Packet Hardening of Intrusion Detection Systems against Smart Adversaries

### 2019-10-25 ex3/paper/paper.tex

In addition to omitting manipulable features we tried to make our network more robust against adversarial samples by augmenting the training set by adversarial flows generated using the \gls{cw}, labeled as additional attacks. However, against our expectations, this approach did not lead to satisfactory results in the sense that the network would learn to classify adversarial samples as attacks. In fact, classification accuracy stayed about constant during the training of the network.

>>>>

\subsection{Adversarial training}
In addition to omitting manipulable features we tried to make our network more robust against adversarial samples by augmenting the training set by adversarial flows generated using the Carlini-Wagner method, labeled as additional attacks.

For this purpose, we added one adversarial sample per attack sample to the training set. Note that, since our used method for obtaining adversarial samples is deterministic, this is the maximum number of adversarial samples possible. With this training set we then alternated retraining of the neural network and optimization of the adversarial samples using gradient descent.

One question which occurs in this process, is how many CPU cycles to spend on network training and adversarial sample optimization. As a natural approach, we decided to use as many backpropagation steps for neural network training as we use for adversarial sample optimization.  For each adversarial sample optimization step, we performed 10 iterations of gradient descent. Hence, all adversarial samples were optimized each 10 epochs of neural network training.

\autoref{fig:avdistance} shows the average distance of a block of adversarial samples from to original, unmodified attack samples throughout the adversarial training procedure. The figure clearly indicates that adversarial training is effective, as the distance gradually increases. Hence, an attacker would have to modify attack samples more and more, eventually rendering the attack unpractical.

However, the figure also shows that an increase of distance can only be achieved after a considerable amount of training. It is, hence, questionable if the gained increase in robustness is enough for reliable attack detection.

\begin{figure}
\includegraphics[width=\columnwidth]{../plots/adv_training/avdistance.pdf}
\caption{Distance of adversarial samples from original attack samples throughout adversarial training.}
\label{fig:avdistance}
\end{figure}

%However, against our expectations, this approach did not lead to satisfactory results in the sense that the network would learn to classify adversarial samples as attacks. In fact, classification accuracy stayed about constant during the training of the network.
